Initial Analysis

### 2022-07-08 Scripts/Initial_Analysis.Rmd
got high seas data

```{r Fun_GetTransResults, eval = F}

@@

stradd_hs_spp <- stradd_data %>% 
  select(taxon_key,category,sf_eez_name = territory, eez_neighbour = neighbour) %>% 
  unique()

# ----------------- #
# Misc.
# ----------------- #

@@

# Dataset to match all SAU names
matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)

@@

Clean_Results_Trans <- my_path("R","EEZ","Clean_Results_Trans.csv", read = T) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(matching_names)

@@

# Used for STRADDLING too
SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(values = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  )

@@

## STRADLING
shared_species <- Tresholded_T_Data %>% 
  left_join(stradd_hs_spp) %>% 
  mutate(category = replace_na(category,"transboundary"))

shared_classification <- shared_species %>% 
  select(taxon_key,category,sf_eez_name) %>% 
  unique()

@@

EEZIDs_List <- my_path("Spa","DBEM", "Updated_EEZList_17June2016.xlsx", read = T) %>% 
  rename(eez_name = name)

# Econ value
Summary_Trans <- SAU_Sampled_Data %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

>>>>

```{r Fun_GetTransResults, eval = T}

@@

stradd_hs_spp <- stradd_data %>% 
  select(taxon_key,category,sf_eez_name = territory, eez_neighbour = neighbour) %>% 
  unique() %>% 
  left_join(matching_names,
            by = "sf_eez_name") %>% 
  select(1:4,fishing_entity_id)

# STRADDLING: Dataset to match all SAU names
matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)
# ----------------- #
# Misc.
# ----------------- #

@@

@@

# STRADDLING
Clean_Results_Trans <- my_path("R","EEZ","Clean_Results_Trans.csv", read = T) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(matching_names)

@@

# Used for STRADDLING too
SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(value = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  ) %>% 
  ## Adding STRADLING component
  left_join(stradd_hs_spp) %>% 
  mutate(category = replace_na(category,"transboundary"))

@@

# shared_classification <- shared_species %>% 
# select(taxon_key,category,fishing_entity_id) %>% 
# unique()

@@

stradd_hs_fentity <- stradd_hs_spp %>% 
  group_by(taxon_key,category, fishing_entity_id) %>% 
  tally() %>% 
  select(-n)

# Econ value WITHOUT HIGH SEAS!!!
Summary_Stradd <-
  SAU_Sampled_Data %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  left_join(stradd_hs_fentity,
            by = c("taxon_key","fishing_entity_id")
  ) %>%
  mutate(Category = ifelse(is.na(category),"trans",category)) %>%
  group_by(Variable,Category) %>%
  summarise(Category_Total = sum(Value, na.rm=T))

Summary_Stradd %>% 
  group_by(Variable) %>% 
  summarise(Total_Trans = sum(Category_Total)) %>% 
  left_join(Summary_Stradd,
            by = "Variable") %>% 
  mutate(
    percentages = (Category_Total/Total_Trans)*100
  )

# Econ value WITH HIGH SEAS!!!

# Used for STRADDLING too
SAU_hs_Data <- bind_rows(
  my_path("G","SAU/SAU HighSeas 18,48,34,27,21,47 v48-0","SAU HighSeas 18,48,34,27,21,47 v48-0.csv",read = T),
  my_path("G","SAU/SAU HighSeas 41,31,58,57,51,88 v48-0","SAU HighSeas 41,31,58,57,51,88 v48-0.csv",read = T),
  my_path("G","SAU/SAU HighSeas 77,67,61,87,81,71 v48-0","SAU HighSeas 77,67,61,87,81,71 v48-0.csv",read = T)
) %>% 
  rename(taxon_name = scientific_name) %>% 
  left_join(taxon_list) %>% 
  filter(
    taxon_key %in% stradd_hs_spp$taxon_key,
    year >= 2005 & year <= 2014,
    catch_type == "Landings",
    reporting_status == "Reported"
  ) %>% 
  # aggregate all gears
  group_by(area_name,fishing_entity,taxon_key,taxon_name,year) %>%
  summarise_at(vars("tonnes","landed_value"),
               .funs = sum,na.rm = T) %>% 
  group_by(area_name,fishing_entity,taxon_key) %>% 
  summarise_at(vars("tonnes","landed_value"),
               .funs = mean,na.rm = T) %>% 
    #filter only straddling species
  semi_join(stradd_hs_fentity,
            by = c("taxon_key")
  ) %>% 
  left_join(stradd_hs_fentity_x) %>% 
  group_by(area_name,fishing_entity,category) %>% 
  summarise_at(vars("tonnes","landed_value"),
               .funs = sum,na.rm = T) %>% 
  gather("variable","value",tonnes:landed_value)

stradd_hs_fentity_x <- stradd_hs_fentity %>% 
  group_by(taxon_key,category) %>% 
  tally()

SAU_hs_Data %>% 
  group_by(variable,category) %>% 
  summarise_at(vars(value),sum) %>% 
  mutate(val_million = value/1000000)

## Figures straddling

### MAP straddling

World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 100)

plot_eez <- stradd_data %>% 
  group_by(eez_name = territory,category) %>% 
  summarise(
    n_species = length(unique(taxon_key))
  )

plot_fao <- stradd_data %>% 
  group_by(fao_name,category) %>% 
  summarise(
    n_species = length(unique(taxon_key))
  )

# FAO

fao_regions <- my_sf("FAO") %>% 
  filter(F_LEVEL == "MAJOR") %>% 
  select(fao_name= NAME_EN,geometry = the_geom) %>% 
  left_join(plot_fao) %>% 
  filter(!is.na(category))

eez_regions <- World_sf %>% 
  left_join(plot_eez) %>% 
  filter(!is.na(category))

st_crs(fao_regions) = 4326
fao_regions <- st_transform(fao_regions, crs = "+proj=eck4")

plot <-ggplot() +
  geom_sf(data = fao_regions, aes(color = n_species, fill = n_species)) +
  geom_sf(data = eez_regions, aes(fill = n_species), color = "grey30") +
  geom_sf(data = World_land_sf, aes(), fill = "grey") +
  scale_fill_viridis() +
  scale_color_viridis() +
  facet_wrap(~category) +
  my_ggtheme_m(leg_pos = "bottom")

ggsave(
  plot = plot,
  width = 17,
  height = 15,
  units = "in",
  filename = "Figures/stradling_maps.png"
)

### Revenue straddling
